When Do You Repeat Yourself?\\ Voices from the Trenches of Linux Kernel Maintainers on Code Duplication

### 2025-11-01 papers/techdebt2026/techdebt.tex
techdebt2026: patchsets: anom-threads: add spacing for styling
There is small spacing remaining at the end of page 5, so add some
`\hfill` just for styling.

Signed-off-by: David Tadokoro <davidbtadokoro@usp.br>

Given the duplicated function pair, we observed that the files in the functions contained multiple other duplications. Thus, we proposed a simple systematic approach to mitigate all the functions duplicated in the context, not just the duplicated function pairs. After approaching the duplications with a systematic strategy, we sent a patch to the AMD development mailing list for the feedback of maintainers, while documenting the process, interactions, and impressions (available in our replication package\footnote{\url{https://doi.org/10.5281/zenodo.17503684}}).

@@

@@

>>>>

Given the duplicated function pair, we observed that the files in the functions contained multiple other duplications. Thus, we proposed a simple systematic approach to mitigate all the functions duplicated in the context, not just the duplicated function pairs. After approaching the duplications with a systematic strategy, we sent a patch to the AMD development mailing list for the feedback of maintainers, while documenting the process, interactions, and impressions (available in our replication package\footnote{\url{https://doi.org/10.5281/zenodo.17503685}}).

@@

\hfill\\

@@

\hfill
